A standard for the scholarly citation of archaeological data as an incentive to data sharing

### 2018-03-12 analysis/paper/paper.Rmd
csl

affiliation:
  - id            : "1"
    institution   : "University of Washington, Seattle, Washington, USA"
  - id            : "2"
    institution   : "University of Georgia,  Athens, Georgia,  USA"

@@

lang              : "english"
class             : "man"

>>>>

affiliation:
  - id            : "1"
    institution   : "University of Washington, Seattle, Washington, USA"
  - id            : "2"B
    institution   : "University of Georgia,  Athens, Georgia,  USA"

@@

lang              : "english"
class             : "man"
csl               : journal-of-archaeological-science.csl
